
# Download modis files MOD44B version 051

There is a folder for each continent or region and in each folder a file "Download.txt" with the files to be downloaded I made a subset for each using the tool <http://reverb.echo.nasa.gov>, and the Python package PyModis is needed


```{r setup, eval=TRUE}

source("R/power_fun.r")



```

# South america (Including Central america)

Up to Mexico, USA is out 

Bounding Box -56.170, -32.695, 33.724, -120.234


```{r SADownload, eval=F}


dataDir <- "~/Dropbox1T/GlobalCriticalForest/southamerica/"

# Download
dm <- down_modis(dataDir,7,14)

# Generate mosaics

mosaic_modis(dataDir,7,14)


```

# North America

USA & Canada

```{r NA, eval=F}

#
# North America
#
dataDir <- "~/Dropbox1T/GlobalCriticalForest/northamerica"

# Download
dm <- down_modis(dataDir,7,15)

# Generate mosaics

mosaic_modis(dataDir,7,15)

```



# Eurasia

Europa include West countries and Russia (excluding both) 

Northasia 
Bounding box 31.053, -168.750, 74.868, -11.602

Countries: Russia Kazakthstan Mongolia


```{r EUS, eval=F}

#
#
dataDir <- "~/Dropbox1T/GlobalCriticalForest/eurasia"

# Download
dm <- down_modis(dataDir,17,29)

# Generate mosaics

mosaic_modis(dataDir,17,29)

```

# Africa

Bounding box -37.160, 56.250, 37.719, -20.391

```{r AF, eval=F}

#
#
dataDir <- "~/Dropbox1T/GlobalCriticalForest/africa"

# Download
dm <- down_modis(dataDir,16,23)

# Generate mosaics

mosaic_modis(dataDir,16,23)

```



# South Asia

Bounding box 0.879, 150.469, 49.838, 25.840

desde h=20 hasta h=30
```{r SAS, eval=T}

#
#
dataDir <- "~/Dropbox1T/GlobalCriticalForest/southasia"

# Download
dm <- down_modis(dataDir,20,30)

# Generate mosaics

mosaic_modis(dataDir,20,30)


```

# Oceania

Bounding box -48.342, 179.648, 7.885, 85.605


27-33

```{r OC, eval=F}

#
#
dataDir <- "~/Dropbox1T/GlobalCriticalForest/oceania"

# Download
dm <- down_modis(dataDir,27,33)

# Generate mosaics

mosaic_modis(dataDir,27,33)


```

