
# Download modis files MOD44B version 051

There is a folder for each continent and in each folder a file "Download.txt" with the files to be downloaded I made a subset for each continent using the tool <http://reverb.echo.nasa.gov>

```{r setup, eval=TRUE}

source("R/power_fun.r")

```

# South america

Up to Panama (Panama is out)

```{r SADownload, eval=F}


dataDir <- "~/Dropbox1T/GlobalCriticalForest/southamerica/"

# Download
# dm <- down_modis(dataDir,9,14)

# Generate mosaics

mosaic_modis(dataDir,9,14)


```

# North America

From USA 

```{r NA, eval=F}

#
# North America
#
dataDir <- "~/Dropbox1T/GlobalCriticalForest/northamerica"

# Download
dm <- down_modis(dataDir,7,15)

# Generate mosaics

mosaic_modis(dataDir,7,15)

```

# Central America

From panama to mexico

```{r CA, eval=F}

#
#
dataDir <- "~/Dropbox1T/GlobalCriticalForest/centralamerica"

# Download
dm <- down_modis(dataDir,7,11)

# Generate mosaics

mosaic_modis(dataDir,7,11)

```


# Europa

Europa include West countries Up to Russia and Turkey (excluding both) 

```{r EU, eval=T}

#
#
dataDir <- "~/Dropbox1T/GlobalCriticalForest/europa"

# Download
dm <- down_modis(dataDir,17,21)

# Generate mosaics

mosaic_modis(dataDir,17,21)

```


# North Asia

Bounding box 40.980, -168.838, 74.868, 27.070

Countries: Russia Kazakthstan Mongolia


```{r NAS, eval=F}

#
#
dataDir <- "~/Dropbox1T/GlobalCriticalForest/northasia"

# Download
dm <- down_modis(dataDir,18,29)

# Generate mosaics

mosaic_modis(dataDir,18,29)

```


# South Asia

Bounding box 0.879, 150.469, 49.838, 25.840

desde h=20 hasta h=30

# Oceania

Bounding box -48.342, 179.648, 7.885, 85.605


# Africa

Bounding box -37.160, 56.250, 37.719, -20.391

