# Contact model to test criteria of maximun patch dynamics 

I use here the following neutral model with power dispersal kernel and only one species:

<https://github.com/lsaravia/Neutral>



## Setup

```{r setup, eval=T }
load(".RData")

if (!require(pacman)) {
	install.packages("pacman") 
	require(pacman)
}
p_load(plyr, dplyr, ggplot2, quantreg, viridis,pander)

panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

oldcd <-getwd()
rasterOptions(tmpdir="~/Academicos/tmp")
source("R/map_fun.r")


```


# Calculate patch statistics for the contact model with different lambda=birth/death at steady state 


```{r patch_steady, echo=FALSE,eval=FALSE}


source("R/Neutral_fun.r")
oldcd<- getwd()
neuBin <- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralPow"
neuBin64<- "~/Dropbox/cpp/CaNew/Neutral/ipsNeutralP64"

makeAnimations <- FALSE

if(makeAnimations){
	# Make simulations
	#
	# (nsp,side,disp,migr,repl,clus="S",time=1000,inter=10,init=1,meta="L",delo=F,sim=T,sedIni=0,modType=4,death=0.2,birth=1,colPal=0,savSed="S") 
	simul_NeutralSpatPatB(nsp,side,alfa,m,ReplRate,"S",time,1,time-15,"U",T,T,999,1,deathRate,birthRate)
	
	# Make animations
	#
	p_load(animation)
	  saveGIF(plot_NeutralSmaxCluster(nsp,side,alfa,m,ReplRate,time,1,time-15,"U",deathRate,birthRate,c("#000000","#76EE00")),       
	          interval = .5,
	          movie.name=paste0("dPer",nsp,"_",side,"R", ReplRate,"L",round(birthRate/deathRate,4),".gif")
	  )

	# Super-critical 
	#
	deathRate <- 0.2
	lambda <- round(birthRate/deathRate,4)
	simul_NeutralSpatPatB(nsp,side,alfa,m,ReplRate,"S",100,5,1,"U",T,T,1,1,deathRate,birthRate)
	
	saveGIF(plot_NeutralSmaxCluster(nsp,side,alfa,m,ReplRate,100,5,1,"U",deathRate,birthRate,c("#000000","#76EE00")),       
	          interval = .5,
	          movie.name=paste0("dPer",nsp,"_",side,"R", ReplRate,"L",round(birthRate/deathRate,4),".gif")
	  )
	
	# Sub-critical
	#
	deathRate <- 0.5
	lambda <- round(birthRate/deathRate,4)
	simul_NeutralSpatPatB(nsp,side,alfa,m,ReplRate,"S",100,5,1,"U",T,T,1,1,deathRate,birthRate)
	
	saveGIF(plot_NeutralSmaxCluster(nsp,side,alfa,m,ReplRate,100,5,1,"U",deathRate,birthRate,c("#000000","#76EE00")),       
	          interval = .5,
	          movie.name=paste0("dPer",nsp,"_",side,"R", ReplRate,"L",round(birthRate/deathRate,4),".gif")
	  )
	
}

#  Simulations of time series and save bin files with patch distributions
#
# (nsp,side,disp,migr,repl,death=0.2,birth=1,simul=T,time=1000,sims=10,meta="U",clus="S",sedIni=0,timeInit=1,timeDelta=10,modType=4,rndSeed=0,delOldSim=FALSE)

#

# Near-critical 
#
alfa=2.17641 # 6.6
side <- 256
nsp <- 1
nSimul <- 1
ReplRate <- 0.0
time <- 100
m =  0.0
birthRate <- 1

# Near critical fragmentation
#
#
# lambda critical = 1.6488
deathRate <- c(0.4,0.39,0.38,0.35,0.41,0.42,0.45)

contact_patch <- data_frame()
contact_fit  <- data_frame()
for(i in 1:length(deathRate))
{ 
	(lambda <- round(birthRate/deathRate[i],4))
	setwd("Results/ContactModel")
	contact_patch <-bind_rows(contact_patch, 
				simul_NeutralTimeSeries_ClustBin(nsp,side,alfa,m,ReplRate,deathRate[i],birthRate,T,time,3,"U","A",3,time-15,1,1,999,T))

	# Fitting distriibutions using Python
	#
	fit <- call_python_powlawfit(".",TRUE) 
	contact_fit <- bind_rows(contact_fit,fit$pyfit)
}
setwd(oldcd)
rm(fit)
save.image()

```

# Calculate fluctuations delta RSmax Make plots and clean up data.frames 

*contact_fit*
*contact_patch*


```{r patch_steady_delta_plots, echo=FALSE,eval=FALSE}

require(dplyr)
require(ggplot2)
require(quantreg)
require(viridis)
require(pander)
panderOptions('table.split.table',Inf)
panderOptions('table.style', 'multiline')

#
# Arrange the data.frame
#

contact_fit <- contact_fit %>% rename(lambda= threshold,Rep=region) %>% mutate(lambda=as.numeric(substring(lambda,2)))

f <- function(df) {
	a <- filter(df, model_name=="PowerExp")
	df$LRT[1] <- a$LRT[1]
	df$pvalue[1] <- a$pvalue[1]
	return(df)
	
}
#undebug(f)
contact_fit <- contact_fit %>% group_by(lambda,Rep,year) %>% do( f(.))

#
# Best models by lambda distribution
#

contact_tot_fit_by_model <- contact_fit %>% group_by(lambda,model_name) %>% mutate(tot_by_model=n()) %>% 
	filter(delta_AICc==0) %>% summarise(best_model_prop=n()/max(tot_by_model)) %>% select(model_name,best_model_prop)  


# Mean of power law exponent
#
contact_fit %>% filter(model_name=="Power") %>% group_by(lambda) %>% summarize(malpha=mean(par1))

# contact_patch <- contact_patch %>% mutate(lambda=round(1/MortalityRate,2))

g <- ggplot(contact_patch, aes(y=RSmax,x=Time,colour=Rep)) +  theme_bw() +
	geom_point(shape=19) +  facet_wrap(~lambda) +  ylab(expression(RS[max]))   + scale_colour_viridis(discrete=F,guide=FALSE)  

g
ggsave("figure/ContactMdl_RSmax_lambda_year.png",width=6,height=6,units="in",dpi=600)

contact_patch<- group_by(contact_patch,lambda,Rep) %>%  mutate(year=as.numeric(Time),
																		 mean_Smax=mean(Smax), 
											  delta_Smax=Smax-mean_Smax,   # Delta max patch
											  delta_RSmax=delta_Smax/TotArea
											  ) 


#
# Fluctuations of RSmax =  Smax - <Smax>/TotArea
#
#
# Test if quantiles are significative
#
require(ggplot2)
require(quantreg)
require(viridis)

contact_qu <-group_by(contact_patch,lambda,Rep) %>% do(data.frame(t(coef(summary(rq((delta_RSmax)~year,data=.,tau=c(.10)),se="boot",R=999))[2,]))) %>% mutate(tau=.10, group="Prop") %>% rename(StdError=Std..Error,t_value=t.value,p_value=Pr...t..)

contact_qu <-bind_rows(contact_qu, group_by(contact_patch,lambda,Rep) %>% 
do(data.frame(t(coef(summary(rq((delta_RSmax)~year,data=.,tau=c(.90)),se="boot",R=999))[2,]))) %>% mutate(tau=.90, group="Prop")%>% rename(StdError=Std..Error,t_value=t.value,p_value=Pr...t..))




#
# Absolute Fluctuations around the mean Smax - <Smax>
#

# Test if quantiles are significative generate table
#
contact_qu <-bind_rows(contact_qu, group_by(contact_patch,lambda,Rep) %>% 
do(data.frame(t(coef(summary(rq((delta_Smax)~year,data=.,tau=c(.10)),se="boot",R=999))[2,]))) %>% mutate(tau=.90, group="Abs")%>% rename(StdError=Std..Error,t_value=t.value,p_value=Pr...t..))

contact_qu <-bind_rows(contact_qu, group_by(contact_patch,lambda,Rep) %>% 
do(data.frame(t(coef(summary(rq((delta_Smax)~year,data=.,tau=c(.90)),se="boot",R=999))[2,]))) %>% mutate(tau=.90, group="Abs")%>% rename(StdError=Std..Error,t_value=t.value,p_value=Pr...t..))

qu1 <- filter(contact_qu, p_value<0.05) %>% arrange( lambda,Rep)
pandoc.table(qu1)


#
# Skewness 
#
ff1<-contact_patch
require(fitdistrplus)
ku <-do(ff1,abs_skewness=(descdist(.$delta_Smax, discrete=FALSE, boot=500))$skewness)
ku <-inner_join(ku,do(ff1,prop_skewness=descdist(.$delta_RSmax, discrete=FALSE, boot=500)$skewness))
ku <- ku %>% mutate(prop_skewness= unlist(prop_skewness), abs_skewness=unlist(abs_skewness))

pandoc.table(ku %>% mutate_if(is.numeric, round, digits=4))

ggplot(filter(ku,threshold %in% c(20,25,30,35,40)), aes(x=regsub,y=abs_skewness,colour=threshold)) + geom_point(shape=22)  +theme_bw()+ ylab(expression(paste("Skewness ",S[max])))+ coord_flip() + scale_colour_viridis(discrete = T) + geom_point(data=filter(ku,threshold==30),colour="red")

ggplot(filter(ku,threshold %in% c(27.5,30,32.5)), aes(x=regsub,y=prop_skewness,colour=threshold)) + geom_point(shape=22)  +theme_bw()+ ylab(expression(paste("Skewness ",S[max])))+ coord_flip() + scale_colour_viridis(discrete = T) + geom_point(data=filter(ku,threshold==30),colour="red")

skewness_threshold <- filter(ku, threshold %in% c(20,25,30,35,40))
rm(ku,ff1)



setwd(oldcd)

```

# Calculate transient responses from subcritical to critical 


```{r patch_steady_transient, echo=FALSE,eval=FALSE}

deathRate <- c(0.4,0.39,0.38,0.35,0.41,0.42,0.45)
1/deathRate


contact_patch_trans <- data_frame()
contact_fit_trans  <- data_frame()
# Sub-critical to critical
#
deathRate <- c(0.45,0.42,0.35,0.38)
for(i in 1:length(deathRate))
{
	(lambdaFrom <- round(birthRate/deathRate[i],4))
	setwd("Results/ContactModel")
	
	simul_NeutralSpatPatB(nsp,side,alfa,m,ReplRate,"S",100,1,100,"U",T,T,3,1,deathRate[i],birthRate)
	(lambdaTo <- round(birthRate/0.4,4))
	
	# Convert BI to SP !!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
	#
	inised <- read_sed(paste0("neuUnif1_256R0L",lambdaFrom,"-0100.sed"))
	
	save_matrix_as_sed(inised,paste0("unifP1_256R",lambdaTo,".sed"),"SP")
	
	
	pat <- 	simul_NeutralTimeSeries_ClustBin(nsp,side,alfa,m,ReplRate,0.4,birthRate,T,16,3,"U","A",3,1,1,1,999,T)
	pat <- pat %>% ungroup() %>% mutate(lambda = lambdaFrom)
	contact_patch_trans <-bind_rows(contact_patch_trans,pat)
	
	fit <- call_python_powlawfit(".",TRUE) 
	contact_fit_trans <- bind_rows(contact_fit_trans, fit$pyfit)
}

setwd(oldcd)

g <- ggplot(contact_patch_trans, aes(y=RSmax,x=Time,colour=Rep)) +  theme_bw() +
	geom_point(shape=19) +  facet_wrap(~lambda) +  ylab(expression(RS[max]))   + scale_colour_viridis(discrete=F,guide=FALSE)  

g
#ggsave("figure/ContactMdl_RSmax_lambda_year.png",width=6,height=6,units="in",dpi=600)

contact_patch_trans<- group_by(contact_patch_trans,lambda,Rep) %>%  mutate(year=as.numeric(Time),
																		 mean_Smax=mean(Smax), 
											  delta_Smax=Smax-mean_Smax,   # Delta max patch
											  delta_RSmax=delta_Smax/TotArea
											  ) 


contact_qu1 <-group_by(contact_patch_trans,lambda,Rep) %>% do(data.frame(t(coef(summary(rq((delta_RSmax)~year,data=.,tau=c(.10)),se="boot",R=999))[2,]))) %>% mutate(tau=.10, group="Prop") %>% rename(StdError=Std..Error,t_value=t.value,p_value=Pr...t..)

contact_qu1 <-bind_rows(contact_qu1, group_by(contact_patch_trans,lambda,Rep) %>% 
do(data.frame(t(coef(summary(rq((delta_RSmax)~year,data=.,tau=c(.90)),se="boot",R=999))[2,]))) %>% mutate(tau=.90, group="Prop")%>% rename(StdError=Std..Error,t_value=t.value,p_value=Pr...t..))

#
# Absolute Fluctuations around the mean Smax - <Smax>
#

# Test if quantiles are significative generate table
#
contact_qu1 <-bind_rows(contact_qu1, group_by(contact_patch_trans,lambda,Rep) %>% 
do(data.frame(t(coef(summary(rq((delta_Smax)~year,data=.,tau=c(.10)),se="boot",R=999))[2,]))) %>% mutate(tau=.90, group="Abs")%>% rename(StdError=Std..Error,t_value=t.value,p_value=Pr...t..))

contact_qu1 <-bind_rows(contact_qu1, group_by(contact_patch_trans,lambda,Rep) %>% 
do(data.frame(t(coef(summary(rq((delta_Smax)~year,data=.,tau=c(.90)),se="boot",R=999))[2,]))) %>% mutate(tau=.90, group="Abs")%>% rename(StdError=Std..Error,t_value=t.value,p_value=Pr...t..))

qu1 <- filter(contact_qu1, p_value<0.05) %>% arrange( lambda,Rep)
pandoc.table(qu1)


save.image()



```

# Read table S2 from Hansen 2013

```{r patch_steady, echo=FALSE,eval=FALSE}


s2 <- read.delim("Results/Hansen2013TableS2.txt", stringsAsFactors = FALSE)
names(s2)

s2 <- mutate(s2,Country=NA)
s2 <- add_row(s2, Country="Indonesia",TotalLoss=157850,TotalGain=69701,
		Treecover2000_lt25=252964,Treecover2000_26.50=68334,Treecover2000_51.75=141996,Treecover2000_76.100=1411892)

```
