
# Test power law estimation

Generate a data set with xmin=1 and alpha=1.59, then add a data set with xmin=20 alpha=1.89


```{r simulData, eval=F, echo=F}


require(poweRlaw)

#Create distribution object              
# 
m = displ$new()
m$setXmin(1);m$setPars(1.59)
# 
#Generate random numbers            #
# 
testP <- dist_rand(m, 1000)
m <- displ$new(testP)
m$setXmin(1) 
(est = estimate_pars(m))
plot(m, main="Alpha=1.59 1000 points")
## Add in the fitted distribution
m$setPars(est$pars)
lines(m, col=2)

# Add some data with different alpha and different xmin
#
m$setXmin(20);m$setPars(1.89)

testP <- c(testP,dist_rand(m, 1000))
m <- displ$new(testP)
m$setXmin(1) 
(est = estimate_pars(m))

plot(m,pch=19, col="violet",main="2000 points a=1.59, xmin=20 a=1.89")
## Add in the fitted distribution
m$setPars(est$pars)
lines(m, col=2)
(est = estimate_xmin(m))

m$setXmin(est$xmin)
m$setPars(est$pars)
lines(m, col=3)

testM <- testP[testP<est$xmin]
mm <- displ$new(testM)
mm$setXmin(1) 
(estM = estimate_pars(mm))

m$setXmin(1)
m$setPars(estM$pars)
lines(m, col=4)

plot(mm)
mm$setPars(estM$pars)
lines(mm, col=4)


```

* it seems to be that the xmin that separates the 2 power laws is correctly estimated, 
* the lower alpha is approximate usign xmin=1, 
* the upper alpha is correctly estimated along xmin. 
* Separating the data x<xmin and estimating alpha doesnt give a correct estimation of the lower alpha.

# Ploting and fitting power law with exponential cutoff to the previous data

```{r testPowLawExp}
len_tP <-length(testP)
tP <- data.frame(psize=sort(testP),Rank=c(len_tP:1)/len_tP)

require(ggplot2)

# Plot with base plot and poweRlaw package
#
require(poweRlaw)
m <- displ$new(testP)
m$setXmin(1) 
(est = estimate_pars(m))
m$setPars(est$pars)
plot(m)
lines(m,col=3)

# Calculate ccdf for power law
#
tP$powl <- 1- dist_cdf(m,tP$psize) 

g <- ggplot(tP, aes(y=(Rank),x=(psize))) +  theme_bw() + geom_point(colour=3,alpha=0.3) + scale_y_log10() +scale_x_log10() + ylab("ccdf")
g + geom_line(aes(y=(powl),x=(psize))) 

# 
source("powerlaw/discpowerexp.R")
source("powerlaw/discexp.R")
source("powerlaw/powerexp.R")


tP$type <- "PowLaw"

# Fit a power law with exponential cutoff
#
#
(est1 <- discpowerexp.fit(testP,1))

# likelihood radio-Test 
#
source("powerlaw/power-law-test.R")

power.powerexp.lrt(est,est1)

# Cumulative power law with exponential cutoff
#
pdiscpowerexp <- function(x,exponent,rate=0,threshold=1)
  {
	# this my.int function allows my CDF to run over vectors
    my.int <- function(y) sum( ddiscpowerexp((threshold:y),exponent,rate,threshold))
    # apply the my.int to each element of x
    sapply(x, FUN=my.int)
  }


cdf_pe <- pdiscpowerexp(unique(tP$psize),est1$exponent,est1$rate)

tP1 <- data.frame(Rank=0,psize=unique(tP$psize),powl=1-cdf_pe,type="PowLawExp")
g + geom_line(aes(y=(powl),x=(psize))) + geom_line(data=tP1,aes(y=(powl),x=(psize)),colour=4) 

# Generete a continous processs discretize it and then... 

```

* I dont like it! 

# Generate a continuous power law, discretize with ceiling and then estimate 


```{r continuousDiscretizedPLaw, eval=F, echo=F}

#Create distribution object for continuous power law             
# 
m = conpl$new()
m$setXmin(1);m$setPars(1.59)
# 
#Generate random numbers            #
# 
testP <- dist_rand(m, 1000)
m <- conpl$new(testP)
m$setXmin(1) 
(est = estimate_pars(m))

# plot
#
m$setPars(est$pars)
plot(m, main="Alpha=1.59 Continuous")

## Add in the fitted distribution
lines(m, col=4)

# Discretize by ceiling
#
testP <- ceiling(testP)

m1 <- displ$new(testP)
m1$setXmin(1) 
(estd = estimate_pars(m1))
m1$setPars(estd$pars)

plot(m1, main="Alpha=1.59 Ceiling")
lines(m1, col=2)

m2 <- conpl$new(testP)
m2$setXmin(1) 
(est = estimate_pars(m2))
m2$setPars(est$pars)
lines(m2, col=3)
# m = conpl$new()
# m$setXmin(1);m$setPars(1.59)
# lines(m2, col=4)

source("powerlaw/powerexp.R")
source("powerlaw/exp.R")

# Fit a power law with exponential cutoff
#
#
(est1 <- powerexp.fit(testP,1))

x <- sort(unique(testP))
y <- ppowerexp(x,1,est1$exponent,est1$rate,lower.tail=F)
lines(x,y,col=4)

# Continuous power law
cdfplot_cpowerlaw(testP,est$pars,est1$exponent,est1$rate)
# Discrete power law
cdfplot_cpowerlaw(testP,estd$pars,est1$exponent,est1$rate)

```

If the process is continuous and then discretized with celing, simulating 30% tree cover rule, estimation with continuous power law seems to be better. 


# Test with real file

```{r realDataTest, eval=T, echo=F}
#

original_bin_files <-"MOD44B.MRTWEB.A2010065.005.Percent_Tree_Cover.tif.bin"
resultsDir <- "~/Dropbox/LabBiologia/MODIS"

or_bi_fi <- paste0(resultsDir,"/",original_bin_files)

connection_file <- file(or_bi_fi, "rb")
data_set <- readBin(connection_file, "double", n = 10^6)

m_m = displ$new(data_set)

m_m$setXmin(1)
(est = estimate_pars(m_m))

m_m$setPars(est$pars)

png(filename="pLawEstimationComp.png",res=300,units = "mm", height=200, width=200)

plot(m_m,xlab="Patch Area",ylab="CCDF")
## Add in the fitted distribution
lines(m_m, col=2)

#
# Test with code from Shalizi <http://tuvalu.santafe.edu/~aaronc/powerlaws/>
#
setwd("~/Dropbox/Projects/CriticalGlobalForest/R")
source("powerlaw/pareto.R")

(est1 <- pareto.fit(data_set,1))

m_m$setXmin(1);m_m$setPars(est1$exponent)

lines(m_m,col=3)

source("powerlaw/powerexp.R")
source("powerlaw/exp.R")

(est2 <- powerexp.fit(data_set,1))
x <- sort(unique(data_set))
y <- ppowerexp(x,1,est2$exponent,est2$rate,lower.tail=F)
lines(x,y,col=4)


model_names <- c("disc powLaw","Cont pow law","Cont pow law exp")
legend("topright",model_names,bty="n",col=seq(2,5),lty=c(1,1,1),cex=0.5)

#cdfplot_cpowerlaw(data_set,est$pars,est1$exponent,est1$rate)

source("powerlaw/power-law-test.R")

power.powerexp.lrt(est1,est2)


dev.off()

source("powerlaw/zeta.R")
(est3 <- zeta.fit(data_set,1))


#
# Fit of power law with exponential cutoff
# 
source("powerlaw/discpowerexp.R")
source("powerlaw/discexp.R")


(est4 <- discpowerexp.fit(data_set,1))

source("powerlaw/power-law-test.R")

power.powerexp.lrt(est3,est4)

# Power law with cut-off is better!!

```



```{r plotTest, eval=T, echo=F}

m = conpl$new()
m$setXmin(1);m$setPars(2.1)
# 
#Generate random numbers            #
# 
testP <- dist_rand(m, 100)
m$setXmin(30);m$setPars(2.5)
testP <- c(testP,dist_rand(m, 100))

m <- conpl$new(testP)
(est = estimate_xmin(m))


po<-plot(m,xlab="Area",ylab="CCDF")
m$setPars(est$pars)
m$setXmin(est$xmin) 
lines(m,col=2)

(est1 <- powerexp.fit(testP,est$xmin))
x <- sort(unique(testP))
x <- x[x>=est1$xmin]
shift <- max(po[po$x>=est1$xmin,]$y)

y <- ppowerexp(x,est1$xmin,est1$exponent,est1$rate,lower.tail=F)*shift
lines(x,y,col=3)

m <- conlnorm$new(x)
m$setXmin(est1$xmin)
(est2<-estimate_pars(m))
m$setPars(est2$pars)
lines(m, col=5)
